Designing Turk Experiments for Visual Statistical Inference

### 2013-06-10 paper_turk.tex
references updated

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

>>>>

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{majumder:2013},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{majumder:2013}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.
